COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
changed one response
So not all participants have the exact same hit rate for 1-back (which would result in a d prime error)

>>>>

```{r Hypothesis_1a, echo=FALSE, message=FALSE, warning=FALSE}

  # H1a: Performance measured by signal detection d’ declines with increasing n-back level.

  # set the number of targets and non-targets, so in case the paradigm will be changed it is easily accessible
  # they are multiplied by 2, because there are two runs per n-back level

  num_targets <- 16*2
  num_nontargets <- 48*2

  # compute index of rows in which the levels change

  levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))

  # set up empty data frame for the loop to feed into

  dprime <- data.frame(subject = character(), level = double(), hitrate = double(), falsealarmrate = double())

  # calculate hits and false alarms per participant

  for (i in 1:(length(levelindex)-1)) {

    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

  # z-transform the hit rate and the false alarm rate

  for (i in 1:4) {

    mean_hitrate <- mean(dprime$hitrate[dprime$level == i])
    sd_hitrate <- sd(dprime$hitrate[dprime$level == i])
    mean_falsealarmrate <- mean(dprime$falsealarmrate[dprime$level == i])
    sd_falsealarmrate <- sd(dprime$falsealarmrate[dprime$level == i])

    for (j in 1:length(which(dprime$level == i))) {

      dprime$hitrate[which(dprime$level == i)[j]] <- (dprime$hitrate[which(dprime$level == i)[j]] - mean_hitrate)/sd_hitrate
      dprime$falsealarmrate[which(dprime$level == i)[j]] <- (dprime$falsealarmrate[which(dprime$level == i)[j]] -
                                                               mean_falsealarmrate)/sd_falsealarmrate
    }
  }

  # calculate d'

  dprime$d <- dprime$hitrate - dprime$falsealarmrate

  # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
